### 2016-08-31 version0.0/asli.tex
Update asli.tex
correct name spellings in acknowledgments

I also would like to thank all my collaborators Prof. E. Peeters, Dr. S. Lianue, and Dr. H. Teimoorinia for not only helping me on moving my projects forward, but also for teaching me how a good scientist work.
Thank you to Dr. D. Stock and Dr. M. Azimlu for all your useful comments.

I would like to thank all my fellow graduate students in Western University: Alex, Aycha, Beth, Boshra, Dimuthu, Fereshteh, Ghazal, Hoori, Javad, Laura, Maryam(s), Matt, Neven, Parshati, Pubu, Robin, Sina, Sham, Taylor and Zahra.
You guys are amazing; you helped me whenever I needed, and I had so much fun hanging out with you.
Thank you Western Physics and Astronomy department staff, especially Clara Buma, Brian Davis, Jodi Guthrie, Henry Leparskas, and Phin Perquin for helping me with the problems an international student can have.

>>>>

I also would like to thank all my collaborators Prof. E. Peeters, Dr. S. Lianou, and Dr. H. Teimoorinia for not only helping me on moving my projects forward, but also for teaching me how a good scientist work.
Thank you to Dr. D. Stock and Dr. M. Azimlu for all your useful comments.

I would like to thank all my fellow graduate students in Western University: Alex, Aycha, Beth, Bushra, Dimuthu, Fereshteh, Ghazal, Hoori, Javad, Laura, Maryam(s), Matt, Neven, Parshati, Pubu, Robin, Sina, Sham, Taylor and Zahra.
You guys are amazing; you helped me whenever I needed, and I had so much fun hanging out with you.
Thank you Western Physics and Astronomy department staff, especially Clara Buma, Brian Davis, Jodi Guthrie, Henry Leparskas, and Phin Perquin for helping me with the problems an international student can have.
